Verifying Demonstrations

### 2017-10-06 protocol.tex
Restructures eligibility and universal verifiability
Adds refs to issues, fixes eligibility and universal

Alice will send her \(pid\) to Jane to start the witness protocol.
Then they do the distance bounding \dots
If Jane is convinced that Alice's secret is within the desired proximity, she 
will compute her witness identifier \(wid\) and witness signature \(wsig\) and 
send them to Alice.

@@

There are three parts to verifying the participation count.
First, we must verify the eligibility of each proof, i.e.\ of all its shares.

\subsubsection{Verifying eligibility}

To verify the eligibility of a proof share, we must verify that \(pid\), \(wid\) 
and \(wsig\) are not just randomly generated numbers but they actually depend on 
the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
We will do this with \ac{NIZK} proofs.

Alice must also provide \iac{NIZK} proof that \(pid = PRF_k(id)\) and that she 
knows a signature by the identity authority on \(k\).
Thus \(pid\) will be used as the unique identifier in the proof shares (and all 
computations below) whereas the \ac{NIZK} proof will be used separately to prove 
the validity (eligibility) of \(pid\).

If the proofs are stored publicly, then an individual can check that their 
proof has been included (committed) there.
Thus \cref{IndividualVerif} is fulfilled.
Similarly for universal verifiability.
If the storage is public, then anyone can download all the proofs, verify their 
eligibility and count them.
Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.

\subsubsection{Universal verifiability}

@@

>>>>

Alice will send her \(pid\) to Jane to start the witness protocol.
Then they do the distance bounding \dots
[See issue \#22 for the discussion.]
If Jane is convinced that Alice's secret is within the desired proximity, she 
will compute her witness identifier \(wid\) and witness signature \(wsig\) and 
send them to Alice.

@@

There are three parts to verifying the participation count.
First, we must verify the eligibility of each proof, i.e.\ of all its shares.
Second, we must count these valid proofs.
Third, each protester must check that their proof is indeed registered so that 
it can be counted.

\subsubsection{Eligibility and universal verifiability}

Universal verifiability (\cref{UniversalVerif}) means that anyone should be able 
to count the valid proofs.
To do this we must be able to verify the eligibility of a proof (i.e.\ of all 
its shares) and then count it if valid.
To verify the eligibility of a proof share, we must verify that \(pid\), \(wid\) 
and \(wsig\) are not just randomly generated numbers but they actually depend on 
the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
We will do this with \ac{NIZK} proofs.
We note that these proofs are not needed until the verification step after the 
protest.
Thus \(pid, wid, wsig\) can be used in the proof shares (and all computations 
above) whereas their respective \ac{NIZK} proof can be computed and published 
after the protest.

Alice must provide \iac{NIZK} proof showing that \(pid = PRF_{k_P}(id)\) and 
that she knows a signature by the identity authority on \(k_P\).
\dots
[Details of how to do this, or maybe that will be in \cref{BuildingBlocks}. See 
issue \#27 for discussion.]

In the same manner, each witness must also provide \iac{NIZK} proofs for \(wid = 
  PRF_{k_W}(pid)\) and \(wsig = PRF_{k_W}(wid, t_s, l)\) as well as that the 
witness knows a signature by the identity authority on \(k_W\).
With these \ac{NIZK} proofs anyone can verify the validity, i.e.\ the 
eligibility, of the proof shares and thus also count them.

@@

If the proofs are stored publicly, then an individual can check that their proof 
has been included (committed) there.
Thus \cref{IndividualVerif} is fulfilled.
